Generalized Bradley-Terry models

### 2025-03-03 inst/jss_hyper3_real.Rnw
start discussing counterstrike

>>>>

\subsection{Counterstrike}

{\em Counter Strike: Global Offensive (CS:GO)} is a multiplayer
first-person shooter game in which two teams of five compete in an
immersive virtual reality combat environment.  Gameplay is typically
complex, including features such as cooperative teamwork, within-team
communication, and real-time strategic fluidity.

Here I analyse a dataset taken from recent esports tournament {\em
  ELEAGUE Major: Boston 2018}.  This Valve-sponsored Major featured 24
elite teams competing for a million dollar prize pool; peak concurrent
viewership exceeded $1.3\times 10^6$, the highest in CS:GO history at
the time.  I study the performance of tournament champions {\em
  Cloud9} who, as underdogs, narrowly defeated aggressive European
rivals {\em FaZe Clan} in the final, which is widely considered to be
the

The dataset used is the deathorder
